---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
source("rcode/00_pkg_functions.R")
```

# flower_duration

We can use the function `plt_summary()` in [`rcode/00_pkg_functions.R`](rcode/00_pkg_functions.R) to plot the records, overlay with grid cells that we can specify resolution, and count the number of cells with enough data.

```{r}
d = readr::read_csv("data/Claytonia virginica_inat.csv") %>% 
  dplyr::select(longitude, latitude, everything()) %>% 
  filter(flowers == 1) %>% 
  drop_na(longitude, latitude) %>% 
  rename(id_iNat = id)

cell_100k = plt_summary(cell_size = 100000, dat = d, n_per_cell = 10)
```

To get the grid cells with enough records specified by `n_per_cell` argument:

```{r}
cell_100k$cells_with_data
```

To get the raw records that to be used (i.e. fall within cells with enough data):

```{r}
cell_100k$dat_to_use
```

To see the plot:

```{r fig.width=8, fig.height=6}
cell_100k$fig
```
